---
title: "Data Report for 2023 HIM Graduate Survey"
author: "Prepared by Laura Collazo"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(qualtRics)
library(tidyverse)
library(tidytext)
library(knitr)
library(kableExtra)

```

```{r read in data, message=FALSE, echo=FALSE}

raw_data <- read_survey("Health+Information+Management+Graduate+Survey+-+2023_March+31,+2023_08.12.csv")

# This filter removes responses from testing and unfinished surveys that were force closed

raw_data <- filter(raw_data, Finished != "FALSE" & DistributionChannel != "preview")

```

```{r write out data, message=FALSE, echo=FALSE}

# This writes out the raw data to provide to the AD

data <- raw_data %>% 
  select(-c(First_Name)) %>% 
  select_if(~!all(is.na(.)))

write.csv(data, "2023_HIM_gradaute_survey_data_2023-3-31.csv")

```

```{css, echo=FALSE}

/*This has been added to hide the unknown level warning before the PLO plots */

pre {
display: none;
}

```

## Response rate

```{r response rate, echo=FALSE}

#The total number of survey recipients needs to manually be set.

total <- 40

n <- nrow(raw_data)

no_response <- total - n

surveys_finished <- (n / total) * 100

unfinished_surveys <- (no_response / total) * 100

response_type <- c("Surveys Finished", "Unfinished Surveys", "Total")
number <- c(n, no_response, total)
percent <- c(surveys_finished, unfinished_surveys, sum(total/total*100))

response_rate <- data.frame(response_type, number, percent)

kable(response_rate, digits = 2) %>% 
  kable_styling("striped")

```

## Margin of error for response rate with a 95% confidence level

#### The margin of error is plus or minus:

```{r margin of error, echo=FALSE}

#confidence level

confidence_level <- 0.95

# margin of error for finite populations

z <- 1.96
p <- n / total 
s<- sqrt(p*(1-p))     
N <- total
nadj <- ((N-1)*n)/(N-n) 
margin_of_error <- (z*s/sqrt(nadj))*100

kable(margin_of_error, col.names = c("margin_of_error"), digits = 2) %>% 
  kable_styling("striped")

```

## Summary statistics

```{r summary statistic function, echo=FALSE}

# create function for stats

summary_stats <- function (mydata, myxvar) {
  select({{mydata}}, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)*100)  %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}

# create function for table

table <- function(mydata) {kable({{mydata}}, digits = 2, row.names = F) %>% 
  kable_styling("striped")
}

#create function for bar plot

bar_plot <- function(myxvar, mytitle){
  suppressWarnings(raw_data %>% 
  select({{myxvar}}) %>% 
    drop_na %>%
  group_by({{myxvar}}) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes({{myxvar}}, percent, 
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent",
       x = NULL) +
 geom_text(labels = scales::percent) + 
 scale_y_continuous(labels = scales::percent))
}

```

### Work status

```{r work status, echo=FALSE}

work_status <- summary_stats(raw_data, Q1)

table(work_status)

bar_plot(Q1, "Work Status")

```

### Is your employment in a health-related field?

```{r employment status, echo=FALSE}

employment_status <- summary_stats(raw_data, Q2)

table(employment_status)

bar_plot(Q2, "Is your employment in a health-related field?")

```

### Job title

```{r job title, echo=FALSE}

job_title_data <- raw_data %>% 
  select(Q3_1) %>% 
  drop_na %>% 
  mutate(Q3_1 = case_when(
    str_detect(Q3_1, "Coding | Coder | coder") ~ "Coder",
    str_detect(Q3_1, "Assistant") ~ "Assistant",
    str_detect(Q3_1, "Supervisor") ~ "Supervisor",
    str_detect(Q3_1, "Manager") ~ "Manager",
    str_detect(Q3_1, "Director") ~ "Director",
    str_detect(Q3_1, "Coordinator") ~ "Coordinator",
    .default = "Other"))

job_title <- summary_stats(job_title_data, Q3_1)

table(job_title)

suppressWarnings(job_title_data %>% 
  select(Q3_1) %>% 
    drop_na %>%
  group_by(Q3_1) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes(Q3_1, percent, 
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = "Categorized Job Titles",
       y = "Percent",
       x = NULL) +
 geom_text(labels = scales::percent) + 
 scale_y_continuous(labels = scales::percent))

```

### Reported employer

```{r reported employer, echo=FALSE}

reported_employer_data <- raw_data %>% 
  mutate(Q3_2 = case_when(
    Q3_2 == "Hackensack meridian" ~ "Hackensack Meridian Health",
    Q3_2 == "New York  Presbyterian hospital" ~ "New York Presbyterian",
    Q3_2 == "NORTHWELL HEALTH" ~ "Northwell Health",
    Q3_2 == "Northwell" ~ "Northwell Health",
    Q3_2 == "NYP BMH" ~ "New York Presbyterian",
    .default = as.character(Q3_2)))

reported_employeer <- summary_stats(reported_employer_data, Q3_2)

table(reported_employeer)

```
### Have you taken the RHIA exam?

```{r taken RHIA, echo=FALSE}

taken_RHIA <- summary_stats(raw_data, Q4) 

table(taken_RHIA)

suppressWarnings(raw_data %>% 
  select(Q4) %>% 
    drop_na %>%
  group_by(Q4) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes(x = "", y = percent, fill = Q4)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) +
  geom_text(aes(label = paste0(scales::percent(percent))), 
            position = position_stack(vjust=0.5)) +
  labs(x = NULL, y = NULL, fill = NULL, title = "Have you taken the RHIA exam?") +
  theme_light() +
  theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank()) +
  scale_fill_manual(values=c("lightgray", "darkgray")))
 
```

### Do you plan on sitting for the RHIA exam?

```{r plan to take RHIA, echo=FALSE}

plan_take_RHIA <- summary_stats(raw_data, Q5) 

table(plan_take_RHIA)

suppressWarnings(raw_data %>% 
  select(Q5) %>% 
    drop_na %>%
  group_by(Q5) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes(x = "", y = percent, fill = Q5)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) +
  geom_text(aes(label = paste0(scales::percent(percent))), 
            position = position_stack(vjust=0.5)) +
  labs(x = NULL, y = NULL, fill = NULL, title = "Do you plan on sitting for the RHIA exam?") +
  theme_light() +
  theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank()) +
  scale_fill_manual(values=c("lightgray", "darkgray")))

```

### When do you plan on taking the RHIA exam?

```{r when plan to take RHIA, echo=FALSE}

when_take_RHIA_data <- raw_data %>% 
  mutate(Q7 = case_when(
    Q7 == "May" ~ "Within 3 months",
    Q7 == "May 7" ~ "Within 3 months",
    Q7 == "June 2022" ~ "Within 3 months",
    Q7 == "Second try in coming month" ~ "Within 3 months",
    Q7 == "As soon a my schedule permits, in the next 6 months" ~ "Within 6 months",
    Q7 == "08/30/2022" ~ "Within 6 months",
    Q7 == "Summer 2022" ~ "Within 6 months",
    Q7 == "Jan 2023" ~ "Within 6 months",
    Q7 == "In the next 6 months" ~ "Within 6 months",
    Q7 == "Summer or Fall" ~ "This year",
    Q7 == "Next year" ~ "Next year",
    Q7 == "next year" ~ "Next year",
    Q7 == "sometime next year" ~ "Next year",
    Q7 == "As soon as I find a job in this field" ~ "Unsure",
    Q7 == "Not sure" ~ "Unsure",
    Q7 == "I don't know." ~ "Unsure",
    Q7 == "2023" ~ "This year",
    Q7 == "2024" ~ "Next year",
    Q7 == "Not sure as yet" ~ "Unsure",
    Q7 == "Not sure working on it. I have had health issues since I graduated" ~ "Unsure",
    Q7 == "june 2023" ~ "Within 3 months",
    .default = as.character(Q7)))

when_take_RHIA <- summary_stats(when_take_RHIA_data, Q7)  %>%
  arrange(fct_relevel(Q7, "Within 3 months", "This year", "Next year", "Unsure"))

table(when_take_RHIA)

suppressWarnings(when_take_RHIA_data %>% 
  select(Q7) %>% 
    drop_na %>%
  group_by(Q7) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes(x = fct_relevel(Q7, "Unsure", "Next year", "This year", "Within 3 months"), percent, 
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = "When do you plan on taking the RHIA exam?",
       y = "Percent",
       x = NULL) +
 geom_text(labels = scales::percent) + 
 scale_y_continuous(labels = scales::percent))

```

## Program Learning Outcomes

```{r program learning outcomes, echo=FALSE}

#create function

plo_summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)*100) %>%
  arrange(fct_relevel({{myxvar}}, "Strongly disagree", "Generally disagree", "Neither agree nor disagree", "Generally agree", "Strongly agree")) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}

# create plo bar plot funciton

plo_bar_plot <- function(myxvar, mytitle){
  suppressWarnings(raw_data %>% 
  select({{myxvar}}) %>% 
    drop_na %>%
  group_by({{myxvar}}) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes(x = fct_relevel({{myxvar}}, "Strongly agree", "Generally agree", "Neither agree nor disagree", "Generally disagree", "Strongly disagree"), 
             percent,
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent",
       x = NULL) +
 geom_text(labels = scales::percent) + 
 scale_y_continuous(labels = scales::percent))
}

```
### Helped me to acquire the knowledge necessary for my job.
```{r Q8_1, echo=FALSE}

plo_1 <- suppressWarnings(plo_summary_stats(Q8_1))

table(plo_1)

plo_bar_plot(Q8_1, "Helped me to acquire the knowledge necessary for my job.")
                 
```

### Prepared me to use sound judgment while functioning in my job.

```{r Q8_2, echo=FALSE, style.display=none}

plo_2 <- suppressWarnings(plo_summary_stats(Q8_2))

table(plo_2)

plo_bar_plot(Q8_2, "Prepared me to use sound judgment while functioning in my job.")


```

### Enabled me to think critically, solve problems, and develop appropriate action steps.

```{r Q8_3, echo=FALSE}

plo_3 <- suppressWarnings(plo_summary_stats(Q8_3))

table(plo_3)

plo_bar_plot(Q8_3, "Enabled me to think critically, solve problems, and develop appropriate action steps.")

```

### Prepared me to communicate effectively within my work setting.

```{r Q8_4, echo=FALSE}

plo_4 <-suppressWarnings(plo_summary_stats(Q8_4))

table(plo_4)

plo_bar_plot(Q8_4, "Prepared me to communicate effectively within my work setting.")

```

### Prepared me to conduct myself in an ethical and professional manner.

```{r Q8_5, echo=FALSE}

plo_5 <- suppressWarnings(plo_summary_stats(Q8_5))

table(plo_5)

plo_bar_plot(Q8_5, "Prepared me to conduct myself in an ethical and professional manner.")

```

### My overall academic experience met my expectations.

```{r Q8_6, echo=FALSE}

plo_6 <- suppressWarnings(plo_summary_stats(Q8_6))

table(plo_6)

plo_bar_plot(Q8_6, "Prepared me to conduct myself in an ethical and professional manner.")

```

## Qualitative Results

#### The following open-ended questions were included in the HIM Graduate Survey:
* What two suggestions would further strengthen the program?
* What knowledge or skills were expected of you upon employment that were not included in the program?
* Please provide comments and suggestions that would help to better prepare future graduates.

#### Qualitative analysis of the responses of these questions, revealed the following themes:
 
```{r text analysis, echo=FALSE, message=FALSE}

text <- raw_data %>% 
  select(c(Q9, Q10, Q11)) 

# create character dataframe

text <- as.character(text)

text_df <- tibble(text = text)

# prepare dataframe for analysis

tidy_text <- text_df %>% 
  unnest_tokens(word, text) # can use this to keep words together: token = "ngrams", n = 3

#remove stop_words

tidy_text <- tidy_text %>% 
  anti_join(stop_words) %>% 
  filter(word != "na")

tidy_text %>% 
  count(word, sort = TRUE)

# order by most common results

tidy_text %>% 
  count(word, sort = TRUE) %>% 
  head(10) %>% 
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = "Top 10 words used most frequently in open-ended responses",
       y = "Count",
       x = NULL) 

```

## Appendix

#### Open-ended responses: Direct quotes as written by respondents.


```{r, echo=FALSE, eval=FALSE}

### Please check the category that reflects your status at the time of this survey - Other (please specify) - there were no responses to this question so it has been hidden

status_other <- raw_data %>% 
  select(Q1_5_TEXT) %>% 
  drop_na()

kable(status_other, digits = 2) %>% 
  kable_styling("striped")

```

### Background information: Job Title

```{r, echo=FALSE}

job_title <- raw_data %>% 
  select(Q3_1) %>% 
  drop_na()

kable(job_title, digits = 2) %>% 
  kable_styling("striped")

```

### Please tell us why you do not plan on taking the RHIA exam

```{r, echo=FALSE}

no_RHIA <- raw_data %>% 
  select(Q6) %>% 
  drop_na()

kable(no_RHIA, digits = 2) %>% 
  kable_styling("striped")

```

### When do you plan on taking the RHIA exam?

```{r, echo=FALSE}

when_RHIA <- raw_data %>% 
  select(Q7) %>% 
  drop_na()

kable(when_RHIA, digits = 2) %>% 
  kable_styling("striped")

```

### What two suggestions would further strengthen the program?

```{r, echo=FALSE}

strengthen_program <- raw_data %>% 
  select(Q9) %>% 
  drop_na()

kable(strengthen_program, digits = 2) %>% 
  kable_styling("striped")
  
```

### What knowledge or skills were expected of you upon employment that were not included in the program?

```{r, echo=FALSE}

expected_skills <- raw_data %>% 
  select(Q10) %>% 
  drop_na()

kable(expected_skills, digits = 2) %>% 
  kable_styling("striped")

```

### Please provide comments and suggestions that would help to better prepare future graduates.

```{r, echo=FALSE}

comments_suggestions <- raw_data %>% 
  select(Q11) %>% 
  drop_na()

kable(comments_suggestions, digits = 2) %>% 
  kable_styling("striped")

```
