---
title: "2023 NURS MS Student Survey Report"
author: "Prepared by Laura Collazo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(qualtRics)
library(tidyverse)
library(kableExtra)

# to avoid messages and warnings

options(dplyr.summarise.inform = FALSE, warn = -1)

```

```{r read in data, message=FALSE, echo=FALSE}

raw_data <- read_survey("MS+in+Nursing+Student+Survey+-+2023_April+5,+2023_03.03.csv")

raw_data <- raw_data %>% 
  mutate(Q4 = as.character(Q4)) %>% 
  mutate(Q40 = case_when(Q40 < 26 ~ "25 and under",
                   Q40 > 25 & Q40 < 31 ~ "26 thru 30",
                   Q40 > 30 & Q40 < 36 ~ "31 thru 35",
                   Q40 > 35 & Q40 < 41 ~ "36 thru 40",
                   Q40 > 40 & Q40 < 46 ~ "41 thru 45",
                   Q40 > 45 & Q40 < 51 ~ "46 thru 50",
                   Q40 > 50 & Q40 < 56 ~ "51 thru 55",
                   Q40 > 55 ~ "56 and over"
                    )) %>%
  mutate(Q74 = recode(Q74, 
      `Other (specify):` = "Other")) %>% 
  mutate(Q74 = recode(Q74, 
      `Outpatient Speciality Clinics ( Example: ENT, GI )` = "Outpatient Speciality Clinics")) %>% 
  mutate(Q30 = recode(Q30, 
      `Other (specify in text box)` = "Other")) %>% 
  mutate(Q32 = recode(Q32,
      `(0) children` = "0",
      `(1) child` = "1",
      `(2) children` = "2",
      `(3 or more) children` = "3 or more")) %>% 
  
# this filter removes responses from testing and responses from open surveys that were force closed
  
  filter(Finished != "FALSE" & DistributionChannel != "preview")

```

This report provides summary statistics and visualizations of student responses to the 2023 NURS MS student survey. The survey was administered through Qualtrics between March 7 - April 4, 2023.

*Note: in some instances the total percent will be slightly above or below 100 as a result of rounding.*

## Response rate

```{r response rate, echo=FALSE}

#The total number of survey recipients needs to manually be set.

total <- 156

n <- nrow(raw_data)

no_response <- total-n

surveys_finished <- (n/total) * 100

unfinished_surveys <- (no_response/total) * 100

percent_total <- surveys_finished + unfinished_surveys

response_type <- c("Surveys Finished", "Unfinished Surveys", "Total")
count <- c(n, no_response, total)
percent <- c(surveys_finished, unfinished_surveys, percent_total)

response_rate <- data.frame(response_type, count, percent)

kable(response_rate, digits = 2) %>% 
  kable_styling()

```

## Margin of error for response rate with a 95% confidence level

#### The margin of error is plus or minus:

```{r margin of error, echo=FALSE}

#confidence level

confidence_level <- 0.95

# margin of error for finite populations

z <- 1.96
p <- n / total 
s<- sqrt(p*(1-p))     
N <- total
nadj <- ((N-1)*n)/(N-n) 
margin_of_error <- (z*s/sqrt(nadj))*100

kable(margin_of_error, col.names = c("margin_of_error"), digits = 2) %>% 
  kable_styling("striped")

```

*Note: The margin of error was calculated with a correction factor for finite populations.*

## Summary Statistics

```{r functions, echo=FALSE}

# create function for summary statistics

summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}

# create function for group summary statistics

group_summary_stats <- function (myxvar, myvaluevar) {
  select(raw_data, {{myxvar}}, `1st_Acad_Plan_Descr`) %>%
    drop_na %>%
  filter(str_detect(`1st_Acad_Plan_Descr`, {{myvaluevar}})) %>% 
  group_by(`1st_Acad_Plan_Descr`, {{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>%  
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}
  
# create function to transpose data

transpose_df <- function(mydata) {{{mydata}} %>%     
    t() %>%      
    as.data.frame() %>%   
    tibble::rownames_to_column(var = "rowname") %>%
    janitor::row_to_names(row_number = 1)
  }

# create function for table

table <- function(mydata) {kable({{mydata}}, row.names = F) %>% 
  kable_styling()
}

# create uni bar plot function

bar_plot <- function(myxvar, mytitle){
  suppressWarnings(raw_data %>% 
  select({{myxvar}}) %>% 
    drop_na %>%
  group_by({{myxvar}}) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes({{myxvar}}, percent, 
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent",
       x = NULL) +
 geom_text(labels = scales::percent) + 
 scale_y_continuous(labels = scales::percent))
}


```

### First NURS Course

#### Term Enrolled in Master's in Nursing Program at CUNY SPS

```{r term, echo=FALSE}
  
term <- summary_stats(Q3) %>%
  arrange(fct_relevel(Q3, "Fall", "Winter", "Spring", "Summer"))

t_term <- transpose_df(term)

table(t_term)

```

#### Year Enrolled in Master's in Nursing Program at CUNY SPS

```{r year, echo=FALSE}
  
year <- summary_stats(Q4)

t_year <- transpose_df(year)

table(t_year)

```
## PLO

```{r PLO functions, echo=FALSE}

# create function

plo_summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>%
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))  %>%
  arrange(fct_relevel({{myxvar}}, "Not at All", "Very Little", "Uncertain", "Well", "Very Well"))
}

# create group function

plo_group_summary_stats <- function (myxvar, myvaluevar) {
select(raw_data, {{myxvar}}, `1st_Acad_Plan_Descr`) %>%
    drop_na %>%
  filter(str_detect(`1st_Acad_Plan_Descr`, {{myvaluevar}})) %>% 
  group_by(`1st_Acad_Plan_Descr`, {{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = Count/sum(Count)) %>% 
  mutate(`% of Total` = as.numeric(`% of Total`)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total'))) %>% 
  arrange(fct_relevel({{myxvar}}, "Not at All", "Very Little", "Uncertain", "Well", "Very Well"))
}

```

### MSN PLO

#### Please indicate how well you feel the Nursing program is preparing you with the ability to: Overall MS Nursing Students

##### Demonstrate effective communication with diverse client populations, disciplines, and staff ensuring optimal health promotion.

```{r plo 1, echo=FALSE}

plo_1 <- plo_summary_stats(PLO_1)

t_plo_1 <- transpose_df(plo_1)

table(t_plo_1)

```

##### Apply leadership skills to guide and educate nursing staff to make sound judgments in the provision of safe, quality nursing care. 

```{r plo 2, echo=FALSE}

plo_2 <- plo_summary_stats(PLO_2)

t_plo_2 <- transpose_df(plo_2)

table(t_plo_2)

```

##### Assume a leadership role in collaborative teams to improve care outcomes and advocate for policy changes through knowledge creation, distribution, and application.

```{r plo 3, echo=FALSE}

plo_3 <- plo_summary_stats(PLO_3)

t_plo_3 <- transpose_df(plo_3)

table(t_plo_3)

```

##### Design health policies that address local and global population health issues. 

```{r plo 4, echo=FALSE}

plo_4 <- plo_summary_stats(PLO_4)

t_plo_4 <- transpose_df(plo_4)

table(t_plo_4)

```

#####  Analyze current and emerging technologies and informatics systems to support safe practice environments, and optimize quality care, cost-effectiveness, and health outcomes.

```{r plo 5, echo=FALSE}

plo_5 <- plo_summary_stats(PLO_5)

t_plo_5 <- transpose_df(plo_5)

table(t_plo_5)

```

##### Demonstrate effective management of patient care across disciplines to ensure best possible health care outcomes, including clinical prevention strategies.

```{r plo 6, echo=FALSE}

plo_6 <- plo_summary_stats(PLO_6)

t_plo_6 <- transpose_df(plo_6)

table(t_plo_6)

```

##### Conduct research, implement evidenced-based care, and quantify the impact on quality and safety.

```{r plo 7, echo=FALSE}

plo_7 <- plo_summary_stats(PLO_7)

t_plo_7 <- transpose_df(plo_7)

table(t_plo_7)

```

##### Demonstrate an understanding of how healthcare delivery systems are organized and financed and how this impacts patient outcomes; and identify the economic, legal, and political factors that influence health care.

```{r plo 8, echo=FALSE}

plo_8 <- plo_summary_stats(PLO_8)

t_plo_8 <- transpose_df(plo_8)

table(t_plo_8)

```

##### Integrate nursing and related sciences in the design, delivery, and evaluation of health care for diverse populations.

```{r plo 9, echo=FALSE}

plo_9 <- plo_summary_stats(PLO_9)

t_plo_9 <- transpose_df(plo_9)

table(t_plo_9)

```

### NURS 611

#### Please note, the following question only applies to students who have taken the course NURS 611. How effective was Shadow Health at facilitating your learning?

```{r nurs_611, echo=FALSE}
  
nurs_611 <- summary_stats(Q35) %>%
  arrange(fct_relevel(Q35, "Not effective at all", "Slightly effective", "Moderately effective", "Very effective", "Extremely effective"))

t_nurs_611 <- transpose_df(nurs_611)

table(t_nurs_611)

```

### Program Satisfaction

#### Does the Nursing Program Blackboard Organization site provide helpful information (e.g. Nursing notes for graduate students) relevant to your progress as a student? 

```{r Q10_total, echo=FALSE}
  
Q10 <- summary_stats(Q10)

t_Q10 <- transpose_df(Q10)

table(t_Q10)

```

#### Overall, I feel that the Nursing faculty and staff provide sufficient support to help me complete my degree. 

```{r Q12_total, echo=FALSE}
  
Q12 <- summary_stats(Q12) %>%
  arrange(fct_relevel(Q12, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"))

t_Q12 <- transpose_df(Q12)

table(t_Q12)

```

#### Overall, how satisfied are you with the CUNY SPS MS in Nursing program?  

```{r Q14_total, echo=FALSE}
  
Q14 <- summary_stats(Q14) %>%
  arrange(fct_relevel(Q14, "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied"))

t_Q14 <- transpose_df(Q14)

table(t_Q14)

```

#### Overall, I feel the college provides sufficient support and resources for me to complete my degree.  

```{r Q20_total, echo=FALSE}
  
Q20 <- summary_stats(Q20) %>%
  arrange(fct_relevel(Q20, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"))

t_Q20 <- transpose_df(Q20)

table(t_Q20)

```
### Campus Services

#### Over the past semester, how satisfied are you with the following campus services? Overall MS Nursing Students

```{r campus summary statistics function, echo=FALSE}

# create function

campus_summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>%
  arrange(fct_relevel({{myxvar}}, "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied", "Did not use",)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}

# create group function

campus_group_summary_stats <- function (myxvar, myvaluevar) {
select(raw_data, {{myxvar}}, `1st_Acad_Plan_Descr`) %>%
    drop_na %>%
  filter(str_detect(`1st_Acad_Plan_Descr`, {{myvaluevar}})) %>% 
  group_by(`1st_Acad_Plan_Descr`, {{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>% 
  mutate(`% of Total` = as.numeric(`% of Total`)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total'))) %>% 
  arrange(fct_relevel({{myxvar}}, "Very Dissatisfied", "Dissatisfied", "Did not use", "Satisfied", "Very Satisfied"))
}

```

##### SPS Help Desk

```{r Q17_HELPDESK, echo=FALSE}

help_desk <- campus_summary_stats(Q17_HELPDESK)

t_help_desk <- transpose_df(help_desk)

table(t_help_desk)

```

##### Career Services

```{r Q17_CAREER_SERVICE, echo=FALSE}

career_service <- campus_summary_stats(Q17_CAREER_SERVICE)

t_career_service <- transpose_df(career_service)

table(t_career_service)

```

##### Financial Aid

```{r Q17_FINANCIAL_AID, echo=FALSE}

financial_aid <- campus_summary_stats(Q17_FINANCIAL_AID)

t_financial_aid <- transpose_df(financial_aid)

table(t_financial_aid)

```

##### Academic Advisement

```{r Q17_ADVISEMENT, echo=FALSE}

advisement <- campus_summary_stats(Q17_ADVISEMENT)

t_advisement <- transpose_df(advisement)

table(t_advisement)

```

##### CUNY SPS e-tutoring services

```{r Q17_E_TUTORING, echo=FALSE}

e_tutoring <- campus_summary_stats(`Q17_E_TUTORING`)

t_e_tutoring <- transpose_df(e_tutoring)

table(t_e_tutoring)

```

##### CUNY SPS Writing Fellows

```{r Q17_WRITING_FELLOW, echo=FALSE}

writing_fellows <- campus_summary_stats(Q17_WRITING_FELLOW)

t_writing_fellows <- transpose_df(writing_fellows)

table(t_writing_fellows)

```
               
##### Library Access at Baruch College

```{r Q17_LIBRARY_ACCESS, echo=FALSE}

library_access <- campus_summary_stats(Q17_LIBRARY_ACCESS)

t_library_access <- transpose_df(library_access)

table(t_library_access)

```

##### Availability of nursing resources at the Baruch College Library

```{r Q17_LIBRARY_RESOURCES, echo=FALSE}

library_resources <- campus_summary_stats(Q17_LIBRARY_RESOURCES)

t_library_resources <- transpose_df(library_resources)

table(t_library_resources)

```

### Employment & Education

#### Are you currently employed as an RN? 

```{r Q70_RN, echo=FALSE}

Q70_RN <- summary_stats(Q70)

t_Q70_RN <- transpose_df(Q70_RN)

table(t_Q70_RN)

```

#### Are you working full-time or part-time?

```{r Q71_employment_status, echo=FALSE}

Q71_employment_status <- summary_stats(Q71)

t_Q71_employment_status <- transpose_df(Q71_employment_status)

table(t_Q71_employment_status)

```
#### Number of years employed in your current position 

```{r Q73_years_employed, echo=FALSE}

Q73_years_employed <- summary_stats(Q73) %>% 
  arrange(fct_relevel(Q73, "Under 1 year", "1-3 years", "4-6 years", "7-9 years", "10-15 years", "Over 15 years"))

t_Q73_years_employed <- transpose_df(Q73_years_employed)

table(t_Q73_years_employed)

```
#### What type of facility do you work in? 

```{r Q74_facility, echo=FALSE}

Q74_facility <- summary_stats(Q74)

t_Q74_facility <- transpose_df(Q74_facility)

table(t_Q74_facility)

```
####  What is the highest degree you have completed?

```{r Q53_degree_completed, echo=FALSE}

Q53_degree_completed <- summary_stats(Q53)

t_Q53_degree_completed <- transpose_df(Q53_degree_completed)

table(t_Q53_degree_completed)

```
#### Degree awarding college: 

```{r Q55_college, echo=FALSE}

Q55_college <- summary_stats(Q55)

t_Q55_college <- transpose_df(Q55_college)

table(t_Q55_college)

```
#### Discipline: 

```{r Q59_discipline, echo=FALSE}

Q59_discipline <- summary_stats(Q59)

t_Q59_discipline <- transpose_df(Q59_discipline)

table(t_Q59_discipline)

```

### Demographics

#### Age range:

```{r Q40_age, echo=FALSE}
  
Q40_age <- summary_stats(Q40)

t_Q40_age <- transpose_df(Q40_age)

table(t_Q40_age)

```

#### Gender Identification:

```{r Q29_gender, echo=FALSE}

Q29_gender <- summary_stats(Q29)

t_Q29_gender <- transpose_df(Q29_gender)
  
table(t_Q29_gender)

```

####  Racial/Ethnic Origin:

```{r Q30_race, echo=FALSE}
  
Q30_race<- summary_stats(Q30) %>% 
  arrange(fct_relevel(Q30, "Asian", "Black/African American","Hispanic", "Native Hawaiian/Pacific Islander", "White", "Multiracial", "Other", "Choose not to answer"))

t_Q30_race <- transpose_df(Q30_race)
  
table(t_Q30_race)

```

#### Marital Status: 

```{r Q31_marital_status, echo=FALSE}
  
Q31_marital_status <- summary_stats(Q31) %>%
  arrange(fct_relevel(Q31, "Single, never married", "Married or domestic partnership", "Separated", "Divorced", "Choose not to answer"))

t_Q31_marital_status <- transpose_df(Q31_marital_status)
  
table(t_Q31_marital_status)

```

####  How many children live with you? 

```{r Q32_children, echo=FALSE}
  
Q32_children <- summary_stats(Q32)

t_Q32_children <- transpose_df(Q32_children)
  
table(t_Q32_children)

```

### Open-Ended

#### Comments about the Nursing Program Blackboard Organization:

```{r Q11_comments_blackboard, echo=FALSE}

comments_blackboard <- raw_data %>% 
  select(Q11) %>% 
  drop_na()

table(comments_blackboard) %>% 
  kable_styling("striped")

```

#### Comments about the Nursing faculty and staff:

```{r Q13_comments_faculty, echo=FALSE}

comments_faculty <- raw_data %>% 
  select(Q13) %>% 
  drop_na()

table(comments_faculty) %>% 
  kable_styling("striped")

```

#### Given your experience in the Nursing program so far, what feedback do you have for the Nursing director and staff?

```{r Q15_comments_feedback, echo=FALSE}

comments_feedback <- raw_data %>% 
  select(Q15) %>% 
  drop_na()

table(comments_feedback) %>% 
  kable_styling("striped")

```

#### Comments about the support services:

```{r Q18_comments_support, echo=FALSE}

comments_support <- raw_data %>% 
  select(Q18) %>% 
  drop_na()

table(comments_support) %>% 
  kable_styling("striped")

```

#### Please explain why you did not use the following service(s):  (e.g., Did not know about it, did not have time, did not need the service, etc.) 

```{r Q19_comments_services, echo=FALSE}

comments_services <- raw_data %>% 
  select(Q19) %>% 
  drop_na()

table(comments_services) %>% 
  kable_styling("striped")

```

#### Comments about the support and resources offered by the college:

```{r Q21_comments_resources, echo=FALSE}

comments_resources <- raw_data %>% 
  select(Q21) %>% 
  drop_na()

table(comments_resources)  %>% 
  kable_styling("striped")

```

#### Employment Details: Current Title:

```{r Q72_3_comments_title, echo=FALSE}

comments_title <- raw_data %>% 
  select(Q72_3) %>% 
  drop_na()

table(comments_title) %>% 
  kable_styling("striped")

```

#### What type of facility do you work in? Other:

```{r Q74_6_TEXT_comments_facility, echo=FALSE}

comments_facility <- raw_data %>% 
  select(Q74_6_TEXT) %>% 
  drop_na()

table(comments_facility) %>% 
  kable_styling("striped")

```

#### College: Other:

```{r Q57_comments_college, echo=FALSE}

comments_college <- raw_data %>% 
  select(Q57) %>% 
  drop_na()

table(comments_college) %>% 
  kable_styling("striped")

```

#### Discipline: Other:

```{r Q61_comments_discipline, echo=FALSE}

comments_discipline <- raw_data %>% 
  select(Q61) %>% 
  drop_na()

table(comments_discipline) %>% 
  kable_styling("striped")

```

#### Racial/Ethnic Origin: Other:

```{r Q30_7_TEXT_comments_race, echo=FALSE}

comments_race <- raw_data %>% 
  select(Q30_7_TEXT) %>% 
  drop_na()

table(comments_race) %>% 
  kable_styling("striped")

```
