---
title: "2023 NURS BS Student Survey Report"
author: "Prepared by Laura Collazo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(qualtRics)
library(tidyverse)
library(kableExtra)

# to avoid messages and warnings

options(dplyr.summarise.inform = FALSE, warn = -1)

```

```{r read in data, message=FALSE, echo=FALSE}

raw_data <- read_survey("BS+in+Nursing+Student+Survey-+2023_April+5,+2023_03.00.csv")

raw_data <- raw_data %>% 
  mutate(Q4 = as.character(Q4)) %>% 
  mutate(Q32 = case_when(Q32 < 26 ~ "25 and under",
                   Q32 > 25 & Q32 < 31 ~ "26 thru 30",
                   Q32 > 30 & Q32 < 36 ~ "31 thru 35",
                   Q32 > 35 & Q32 < 41 ~ "36 thru 40",
                   Q32 > 40 & Q32 < 46 ~ "41 thru 45",
                   Q32 > 45 & Q32 < 51 ~ "46 thru 50",
                   Q32 > 50 & Q32 < 56 ~ "51 thru 55",
                   Q32 > 55 ~ "56 and over"
                    )) %>% 
  mutate(Q21 = recode(Q21, 
      `Other (specify):` = "Other")) %>% 
  mutate(Q21 = recode(Q21, 
      `Outpatient Speciality Clinics ( Example: ENT, GI )` = "Outpatient Speciality Clinics")) %>% 
  mutate(Q26 = recode(Q26, 
      `Other (specify in text box)` = "Other")) %>% 
  mutate(Q28 = recode(Q28,
      `(0) dependent` = "0",
      `(1) dependent` = "1",
      `(2) dependents` = "2",
      `(3 or more) dependents` = "3 or more")) %>% 
  
# this filter removes responses from testing and responses from open surveys that were force closed
  
  filter(Finished != "FALSE" & DistributionChannel != "preview") 

```

This report provides summary statistics and visualizations of student responses to the 2023 NURS BS student survey. The survey was administered through Qualtrics between March 7 - April 4, 2023.

*Note: in some instances the total percent will be slightly above or below 100 as a result of rounding.*

## Response rate

```{r response rate, echo=FALSE}

#The total number of survey recipients needs to manually be set.

total <- 347

n <- nrow(raw_data)

no_response <- total-n

surveys_finished <- (n/total) * 100

unfinished_surveys <- (no_response/total) * 100

percent_total <- surveys_finished + unfinished_surveys

response_type <- c("Surveys Finished", "Unfinished Surveys", "Total")
count <- c(n, no_response, total)
percent <- c(surveys_finished, unfinished_surveys, percent_total)

response_rate <- data.frame(response_type, count, percent)

kable(response_rate, digits = 2) %>% 
  kable_styling()

```

## Margin of error for response rate with a 95% confidence level

#### The margin of error is plus or minus:

```{r margin of error, echo=FALSE}

#confidence level

confidence_level <- 0.95

# margin of error for finite populations

z <- 1.96
p <- n / total 
s<- sqrt(p*(1-p))     
N <- total
nadj <- ((N-1)*n)/(N-n) 
margin_of_error <- (z*s/sqrt(nadj))*100

kable(margin_of_error, col.names = c("margin_of_error"), digits = 2) %>% 
  kable_styling("striped")

```

*Note: The margin of error was calculated with a correction factor for finite populations.*

## Summary statistics

```{r functions, echo=FALSE}

# create function for summary statistics

summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total'))) 
}

# create function to transpose data

transpose_df <- function(mydata) {{{mydata}} %>%     
    t() %>%      
    as.data.frame() %>%   
    tibble::rownames_to_column(var = "rowname") %>%
    janitor::row_to_names(row_number = 1)
  }

# create function for table

table <- function(mydata) {kable({{mydata}}, digits = 2, row.names = F) %>% 
  kable_styling()
}

# create bar plot function

bar_plot <- function(myxvar, mytitle){
  suppressWarnings(raw_data %>% 
  select({{myxvar}}) %>% 
    drop_na %>%
  group_by({{myxvar}}) %>% 
  summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>% 
  ggplot(aes({{myxvar}}, percent, 
             label=scales::percent(percent))) +
  geom_col(fill="lightgray") +
  coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent of total",
       x = NULL) +
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5)))
}

```

### First NURS Course

#### Term of First Nursing Course

```{r Q3, echo=FALSE}
  
semester_first <- summary_stats(Q3) %>%
  arrange(fct_relevel(Q3, "Fall", "Winter", "Spring", "Summer"))

t_semester_first <- transpose_df(semester_first)

table(t_semester_first) 

raw_data %>% 
  select(Q3) %>% 
    drop_na() %>% 
  group_by(Q3) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q3, "Fall", "Winter", "Spring", "Summer"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Term of first NURS course",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### Year of First Nursing Course

```{r Q4, echo=FALSE}

year_first <- summary_stats(Q4)

t_year_first <- transpose_df(year_first) 

table(t_year_first)

bar_plot(Q4, "Year of first NURS course")

```

### Employment & Education

#### Are you currently employed as an RN?

```{r Q19, echo=FALSE}

employed_rn <- summary_stats(Q19)

t_employed_rn <- transpose_df(employed_rn)

table (t_employed_rn)

bar_plot(Q19, "Are you currently employed as an RN?")

```

#### Are you working full-time or part-time?

```{r Q20, echo=FALSE}

employed_status <- summary_stats(Q20)

t_employed_status <- transpose_df(employed_status)

table(t_employed_status)

bar_plot(Q20, "Are you working full-time or part-time?")


```

#### Number of years employed in your current position

```{r Q33, echo=FALSE}

employed_years <- summary_stats(Q33) %>%
  arrange(fct_relevel(Q33, "under 1 year", "1-3 years", "4-6 years", "7-9 years", "10-15 years", "Over 15 years"))

t_employed_years <- transpose_df(employed_years)

table(t_employed_years)

raw_data %>% 
  select(Q33) %>% 
    drop_na() %>% 
  group_by(Q33) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q33, "under 1 year", "1-3 years", "4-6 years", "7-9 years", "10-15 years", "Over 15 years"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Number of years employed in current position",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### What type of facility do you work in?

```{r Q21, echo=FALSE}

employed_facility <- summary_stats(Q21)

t_employed_facility <- transpose_df(employed_facility)

table(t_employed_facility)

bar_plot(Q21, "What type of facility do you work in?")

```

#### What is the highest degree you have completed?

```{r Q22, echo=FALSE}

degree_type <- summary_stats(Q22)

t_degree_type <- transpose_df(degree_type)

table(t_degree_type)

bar_plot(Q22, "What is the highest degree you have completed?")

```

#### Please tell us about the college you earned your degree from:

```{r Q23, echo=FALSE}

degree_location <- summary_stats(Q23)

t_degree_location <- transpose_df(degree_location)

table(t_degree_location)

bar_plot(Q23, "What college did you earn your degree from?")

```

#### Please tell us about the discipline you earned your degree in:

```{r Q30, echo=FALSE}

degree_discipline <- summary_stats(Q30)

t_degree_discipline <- transpose_df(degree_discipline)

table(t_degree_discipline)

bar_plot(Q30, "What discipline did you earn your degree in?")

```

### PLO

#### Please indicate how well you feel the Nursing program is preparing you with the abilities to:

```{r PLO summary statistics function, echo=FALSE}

# create function

plo_summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>%
  arrange(fct_relevel({{myxvar}}, "Not at All", "Very Little", "Uncertain", "Well", "Very Well")) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total'))) 
}

# create plot function

plo_bar_plot <- function(myxvar, mytitle) {
  raw_data %>% 
  select({{myxvar}}) %>% 
      drop_na() %>% 
  group_by({{myxvar}}) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel({{myxvar}}, "Not at All", "Very Little", "Uncertain", "Well", "Very Well"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))
  
}

```

##### Provide care that is cognizant of and respectful of the patients's cultural beliefs.

```{r plo_1, echo=FALSE}

plo_1 <- plo_summary_stats(PLO_1)

t_plo_1 <- transpose_df(plo_1)

table(t_plo_1)

plo_bar_plot(PLO_1, "How well do you feel the Nursing program is preparing you with the abilities to\n provide care that is cognizant of and respectful of the patients's cultural beliefs?")

```

##### Practice the profession of nursing based on a set of core values which incorporate a humanitarian, altruistic and social justice perspective.

```{r plo_2, echo=FALSE}

plo_2 <- plo_summary_stats(PLO_2)

t_plo_2 <- transpose_df(plo_2)

table(t_plo_2)

plo_bar_plot(PLO_2, "How well do you feel the Nursing program is preparing you with the abilities to\n practice the profession of nursing based on a set of core values which\n incorporate a humanitarian, altruistic and social justice perspective?")

```

##### Communicate effectively with patients, families, communities and other healthcare providers to promote health.

```{r plo_3, echo=FALSE}

plo_3 <- plo_summary_stats(PLO_3)

t_plo_3 <- transpose_df(plo_3)

table(t_plo_3)

plo_bar_plot(PLO_3, "How well do you feel the Nursing program is preparing you with the abilities to\n communicate effectively with patients, families, communities and other\n healthcare providers to promote health?")

```

##### Integrate reliable evidence to provide the highest quality patient care.

```{r plo_4, echo=FALSE}

plo_4 <- plo_summary_stats(PLO_4)

t_plo_4 <- transpose_df(plo_4)

table(t_plo_4)

plo_bar_plot(PLO_4, "How well do you feel the Nursing program is preparing you with the abilities to\n integrate reliable evidence to provide the highest quality patient care?")

```

##### Advocate for relevant local and global healthcare policy.

```{r plo_5, echo=FALSE}

plo_5 <- plo_summary_stats(PLO_5)

t_plo_5 <- transpose_df(plo_5)

table(t_plo_5)

plo_bar_plot(PLO_5, "How well do you feel the Nursing program is preparing you with the abilities to\n advocate for relevant local and global healthcare policy?")

```

##### Apply leadership and management concepts to ensure best possible health care outcomes.

```{r plo_6, echo=FALSE}

plo_6 <- plo_summary_stats(PLO_6)

t_plo_6 <- transpose_df(plo_6)

table(t_plo_6)

plo_bar_plot(PLO_6, "How well do you feel the Nursing program is preparing you with the abilities to\n apply leadership and management concepts to ensure best possible health care\n outcomes?")

```

##### Use critical thinking skills to make sound clinical judgment.

```{r plo_7, echo=FALSE}

plo_7 <- plo_summary_stats(PLO_7)

t_plo_7 <- transpose_df(plo_7)

table(t_plo_7)

plo_bar_plot(PLO_7, "How well do you feel the Nursing program is preparing you with the abilities to\n use critical thinking skills to make sound clinical judgment?")

```

##### Utilize and manage all available health information technology to provide safe and effective patient care.

```{r plo_8, echo=FALSE}

plo_8 <- plo_summary_stats(PLO_8)

t_plo_8 <- transpose_df(plo_8)

table(t_plo_8)

plo_bar_plot(PLO_8, "How well do you feel the Nursing program is preparing you with the abilities to\n utilize and manage all available health information technology to provide safe\n and effective patient care?")

```

##### Participate in patient safety and quality initiatives within the context of an inter-professional team.

```{r Q5_9, echo=FALSE}

plo_9 <- plo_summary_stats(Q5_9)

t_plo_9 <- transpose_df(plo_9)

table(t_plo_9)

plo_bar_plot(Q5_9, "How well do you feel the Nursing program is preparing you with the abilities to\n participate in patient safety and quality initiatives within the context of an\n inter-professional team?")

```

### Program Satisfaction

#### Does the Nursing Program Blackboard site provide helpful information relevant to your progress as a student?

```{r Q6, echo=FALSE}

blackboard <- summary_stats(Q6)

t_blackboard <- transpose_df(blackboard)

table(t_blackboard)

bar_plot(Q6, "Does the Nursing Program Blackboard site provide helpful information relevant to\n your progress as a student?")

```

#### Overall, I feel that the Nursing faculty and staff provide sufficient support to help me complete my degree.

```{r Q8, echo=FALSE}

support <- summary_stats(Q8) %>% 
  arrange(fct_relevel(Q8, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"))

t_support <- transpose_df(support)

table(t_support)

raw_data %>% 
  select(Q8) %>% 
    drop_na() %>% 
  group_by(Q8) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q8, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Overall, I feel that the Nursing faculty and staff provide sufficient support\n to help me complete my degree.",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### Overall, how satisfied are you with the CUNY SPS RN to BS in Nursing program?

```{r Q10, echo=FALSE}

satisfaction <- summary_stats(Q10) %>% 
  arrange(fct_relevel(Q10, "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied"))

t_satisfaction <- transpose_df(satisfaction)

table(t_satisfaction)

raw_data %>% 
  select(Q10) %>% 
    drop_na() %>% 
  group_by(Q10) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q10, "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Overall, how satisfied are you with the CUNY SPS RN to BS in\n Nursing program?",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### Overall, I feel that the college provides sufficient support and resources for me to complete my degree.

```{r Q16, echo=FALSE}

resources <- summary_stats(Q16) %>% 
  arrange(fct_relevel(Q16, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"))

t_resources <- transpose_df(resources)

table(t_resources)

raw_data %>% 
  select(Q16) %>% 
    drop_na() %>% 
  group_by(Q16) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q16, "Strongly Disagree", "Disagree", "Agree", "Strongly Agree"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Overall, I feel that the college provides sufficient support and resources for\n me to complete my degree.",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

### NURS 301

#### The following question only applies to students who have taken the course NURS 301. How effective/ineffective was Shadow Health at facilitating your learning?

```{r Q34, echo=FALSE}

nurs_301 <- summary_stats(Q34) %>% 
  arrange(fct_relevel(Q34, "Not effective at all", "Slightly effective", "Moderately effective", "Very effective", "Extremely effective"))

t_nurs_301 <- transpose_df(nurs_301)

table(t_nurs_301)

raw_data %>% 
  select(Q34) %>% 
    drop_na() %>% 
  group_by(Q34) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q34, "Not effective at all", "Slightly effective", "Moderately effective", "Very effective", "Extremely effective"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "How effective/ineffective was Shadow Health at facilitating your learning?",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

### Campus Services

#### Over the past semester, how satisfied are you with the following campus services?

```{r campus summary statistics function, echo=FALSE}

# create function

campus_summary_stats <- function (myxvar) {
  select(raw_data, {{myxvar}}) %>%
    drop_na %>%
  group_by({{myxvar}}) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>%
  arrange(fct_relevel({{myxvar}}, "Did not use", "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied")) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))
}

# create plot function

campus_bar_plot <- function(myxvar, mytitle) {
  raw_data %>% 
  select({{myxvar}}) %>% 
      drop_na() %>% 
  group_by({{myxvar}}) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel({{myxvar}}, "Did not use", "Very Dissatisfied", "Dissatisfied", "Satisfied", "Very Satisfied"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = mytitle,
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))
  
}

```

##### SPS Help Desk

```{r Q13_HelpDesk, echo=FALSE}

help_desk <- campus_summary_stats(Q13_HelpDesk)

t_help_desk <- transpose_df(help_desk)

table(t_help_desk)

campus_bar_plot(Q13_HelpDesk, "Over the past semester, how satisfied are you with the following\n campus service: SPS Help Desk")

```

##### Career Services

```{r Q13_Career_Service, echo=FALSE}

career_service <- campus_summary_stats(Q13_Career_Service)

t_career_service <- transpose_df(career_service)

table(t_career_service)

campus_bar_plot(Q13_Career_Service, "Over the past semester, how satisfied are you with the following\n campus service: Career Services")

```

##### Financial Aid

```{r Q13_FinancialAid, echo=FALSE}

financial_aid <- campus_summary_stats(Q13_FinancialAid)

t_financial_aid <- transpose_df(financial_aid)

table(t_financial_aid)

campus_bar_plot(Q13_FinancialAid, "Over the past semester, how satisfied are you with the following\n campus service: Financial Aid")

```

##### Academic Advisement

```{r Q13_Advisement, echo=FALSE}

advisement <- campus_summary_stats(Q13_Advisement)

t_advisement <- transpose_df(advisement)

table(t_advisement)

campus_bar_plot(Q13_Advisement, "Over the past semester, how satisfied are you with the following\n campus service: Academic Advisement")

```

##### CUNY SPS e-tutoring services

```{r Q13_e-tutoring, echo=FALSE}

e_tutoring <- campus_summary_stats(`Q13_e-tutoring`)

t_e_tutoring <- transpose_df(e_tutoring)

table(t_e_tutoring)

campus_bar_plot(`Q13_e-tutoring`, "Over the past semester, how satisfied are you with the following\n campus service: CUNY SPS e-tutoring services")

```

##### CUNY SPS Writing Fellows

```{r Q13_WritingFellows, echo=FALSE}

writing_fellows <- campus_summary_stats(Q13_WritingFellows)

t_writing_fellows <- transpose_df(writing_fellows)

table(t_writing_fellows)

campus_bar_plot(Q13_WritingFellows, "Over the past semester, how satisfied are you with the following\n campus service: CUNY SPS Writing Fellows")

```

##### Library Access at Baruch College

```{r Q13_LibraryAccess, echo=FALSE}

library_access <- campus_summary_stats(Q13_LibraryAccess)

t_library_access <- transpose_df(library_access)

table(t_library_access)

campus_bar_plot(Q13_LibraryAccess, "Over the past semester, how satisfied are you with the following\n campus service: Library Access at Baruch College")

```

##### Availability of nursing resources at the Baruch College Library

```{r Q13_LibraryResources, echo=FALSE}

library_resources <- campus_summary_stats(Q13_LibraryResources)

t_library_resources <- transpose_df(library_resources)

table(t_library_resources)

campus_bar_plot(Q13_LibraryResources, "Over the past semester, how satisfied are you with the following\n campus service: Availability of nursing resources at the Baruch College Library")

```

### Demographics

#### Age range:

```{r Q32, echo=FALSE}

# Age range (report from last year is incorrect!)

age <- raw_data %>% 
  select(Q32) %>% 
  drop_na %>%
  group_by(Q32) %>%
summarise(Count = n()) %>%
  mutate(`% of Total` = round(Count/sum(Count)*100, 2)) %>% 
   bind_rows(summarise(., across(where(is.numeric), sum),
                          across(where(is.character), ~'Total')))

t_age <- transpose_df(age)

table(t_age)

bar_plot(Q32, "Age range of Nursing BS survey respondents")

```

#### Gender identification:

```{r Q25, echo=FALSE}

gender <- summary_stats(Q25) %>% 
  arrange(fct_relevel(Q25, "Female", "Male", "Choose not to answer"))

t_gender <- transpose_df(gender)

table(t_gender)

raw_data %>% 
  select(Q25) %>% 
    drop_na() %>% 
  group_by(Q25) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q25, "Female", "Male", "Choose not to answer"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Gender identification of Nursing BS survey respondents",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### Racial/Ethnic Origin:

```{r Q26, echo=FALSE}

race <- summary_stats(Q26) %>% 
  arrange(fct_relevel(Q26, "Asian", "Black/African American","Hispanic", "Native Hawaiian/Pacific Islander", "White", "Multiracial", "Other", "Choose not to answer"))

t_race <- transpose_df(race)

table(t_race)

raw_data %>% 
  select(Q26) %>% 
    drop_na() %>% 
  group_by(Q26) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q26, "Asian", "Black/African American","Hispanic", "Native Hawaiian/Pacific Islander", "White", "Multiracial", "Other", "Choose not to answer"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Racial/Ethnic origin of Nursing BS survey respondents",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### Marital Status:

```{r Q27, echo=FALSE}

marital_status <- summary_stats(Q27) %>% 
  arrange(fct_relevel(Q27, "Single, never married", "Married or domestic partnership", "Separated", "Divorced", "Choose not to answer"))

t_marital_status <- transpose_df(marital_status)

table(t_marital_status)

raw_data %>% 
  select(Q27) %>%
    drop_na() %>% 
  group_by(Q27) %>%
summarise(count = n()) %>%
  mutate(percent = count/sum(count)) %>%
  ggplot(aes(x = fct_relevel(Q27, "Single, never married", "Married or domestic partnership", "Separated", "Divorced", "Choose not to answer"), y = percent)) + 
  geom_col(fill="lightgray") +
coord_flip() +
  theme_light() +
  labs(title = "Marital Status of Nursing BS survey respondents",
       y = "Percent of total",
       x = NULL) + 
 scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(percent), hjust = .5))

```

#### How many dependents live with you?

```{r Q28, echo=FALSE}

dependents <- summary_stats(Q28)

t_dependents <- transpose_df(dependents)

table(t_dependents)

bar_plot(Q28, "Number of dependents living with Nursin BS survey respondents")

```

### Open-Ended

```{r Q7, echo=FALSE}

comments_blackboard <- raw_data %>% 
  select(Q7) %>% 
  drop_na() %>% 
  rename("Comments about the Nursing Program Blackboard Organization:" = Q7)

table(comments_blackboard) %>% 
  kable_styling("striped")

```

```{r Q9, echo=FALSE}

comments_faculty <- raw_data %>% 
  select(Q9) %>% 
  drop_na() %>% 
  rename("Comments about the Nursing faculty and staff:" = Q9)

table(comments_faculty) %>% 
  kable_styling("striped")

```

```{r Q11, echo=FALSE}

comments_feedback <- raw_data %>% 
  select(Q11) %>% 
  drop_na() %>% 
  rename("Given your experience in the Nursing program so far, what feedback do you have for the Nursing director and staff?" = Q11)

table(comments_feedback) %>% 
  kable_styling("striped")

```

```{r Q14, echo=FALSE}

comments_support <- raw_data %>% 
  select(Q14) %>% 
  drop_na()  %>% 
  rename("Comments about support services:" = Q14)

table(comments_support) %>% 
  kable_styling("striped")

```

```{r Q15, echo=FALSE}

comments_services <- raw_data %>% 
  select(Q15) %>% 
  drop_na() %>% 
  rename("Please explain why you did not use the following service(s): (e.g., Did not know about it, did not have time, did not need the service, etc." = Q15)

table(comments_services) %>% 
  kable_styling("striped")

```

```{r Q17, echo=FALSE}

comments_resources <- raw_data %>% 
  select(Q17) %>% 
  drop_na() %>% 
  rename("Comments about the support and resources offered by the college:" = Q17)

table(comments_resources) %>% 
  kable_styling("striped")

```

```{r Q29_3, echo=FALSE}

comments_title <- raw_data %>% 
  select(Q29_3) %>% 
  drop_na() %>% 
  rename("Employment Details: Current Title:" = Q29_3)

table(comments_title) %>% 
  kable_styling("striped")

```

```{r Q21_6_TEXT, echo=FALSE}

comments_facility <- raw_data %>% 
  select(Q21_6_TEXT) %>% 
  drop_na() %>% 
  rename("What type of facility do you work in? Other:" = Q21_6_TEXT)

table(comments_facility) %>% 
  kable_styling("striped")

```

```{r Q31, echo=FALSE}

comments_college <- raw_data %>% 
  select(Q31) %>% 
  drop_na() %>% 
  rename("College: Other:" = Q31)

table(comments_college) %>% 
  kable_styling("striped")

```

```{r Q35, echo=FALSE}

comments_discipline <- raw_data %>% 
  select(Q35) %>% 
  drop_na() %>% 
  rename("Discipline: Other:" = Q35)

table(comments_discipline) %>% 
  kable_styling("striped")

```

```{r Q26_7_TEXT, echo=FALSE}

comments_race <- raw_data %>% 
  select(Q26_7_TEXT) %>% 
  drop_na() %>% 
  rename("Racial/Ethnic Origin: Other:" = Q26_7_TEXT)

table(comments_race) %>% 
  kable_styling("striped")

```
